\tool: Revisiting BadUSB with Type-C

### 2021-01-28 WOOT/Files/experiment.tex
[experiment] fix figure
[experiment] figure of PBS
fix some suggestions in imple

\textit{Setup.} \fengwei{I would suggest to add references for devices such as
Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B as the embedded
computer inside \tool, which is powerful enough to process video data and has
onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board
with USB protocol support. This Atmel chip is able to emulate most HID devices
with our modified firmware. About the USB 3.x hub, we uses one from the
Yamazawa, which supports HDMI, USB 2.0, and many other exported peripheral.
Apart from these essential parts, we also uses an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
2, 3, 4, and 5?}

\begin{figure}[t]
	\centering
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}
	\caption{\tool}
	\label{fig:PBS_products}
\end{figure}

>>>>

\textit{Setup.} \fengwei{I would suggest to add references for devices such as
Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
computer inside \tool, which is powerful enough to process video data and has
onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board~\cite{atmel}
with USB protocol support. This Atmel chip is able to emulate most HID devices
with our modified firmware. About the USB 3.x hub, we uses one from the
UGREEN, which supports HDMI, USB 2.0, and many other exported peripheral.
Apart from these essential parts, we also uses an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
2, 3, 4, and 5?}

\begin{figure}[t]
	\centering
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}
	\caption{\tool}
	\label{fig:armory}
\end{figure}
